Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2015-10-20 manuscript/text_reuse.tex
another small update

\usepackage{graphicx} % to include pictures
\usepackage{subfig} % create subfigures within figures
\usepackage{pdflscape} % e.g. to rotate one page of the document
\usepackage{booktabs} % make better looking tabels with different line types and stuff
\usepackage[left=2.5cm,right=3cm,top=3cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr} % for pages with custom headers and footers
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{pa}

@@

@@

\item Extract state  \& bill \# from tables (FL) -- lower priority
    \begin{enumerate}
        \item Didn't do this yet, let's first check how many are potentially suitable and then probably better to do by hand
    \end{enumerate}
\item See tasks in analysis -- create metadata file and dyadic file, then put them on the ACI (FL).
    \begin{enumerate}
        \item We have a preliminary dyadic file for all similar bill pairs and their alignment scores (this is from the LID approach: each bill is only compared to the 100 most similar ones)
        \item Matt transfering the database to a new server at the moment, it is therefore unavailable. Should be online again sometime today.
    \end{enumerate}
\item Store MALP data on ACI and make sure the identifiers match those in the bill data (FL). 
    \begin{enumerate}
        \item data is on aci
        \item Most Legislators can probably be matched by Name, Pary, State, Time in Office
    \end{enumerate}
\item Put policy diffusion data in project folder on ACI (BD).
\end{itemize}

>>>>

\usepackage{graphicx} % to include pictures
\usepackage{subfig} % create subfigures within figures
\usepackage{pdflscape} % e.g. to rotate one page of the document
\usepackage{booktabs} % make better looking tabels with different line types and stuff
\usepackage[left=2.5cm,right=3cm,top=3cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr} % for pages with custom headers and footers
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{hyperref}

@@

In order to detect text reuse between bills we follow \citet{wilderson2015tracing} and use the Smith-Waterman local alignment algorithm \citep{smith1981identification}.

@@

\item Extract state  \& bill \# from tables (FL) -- lower priority
    \begin{enumerate}
        \item Didn't do this yet, let's first check how many are potentially suitable and then probably better to do by hand
    \end{enumerate}
\item See tasks in analysis -- create metadata file and dyadic file, then put them on the ACI (FL).
    \begin{enumerate}
        \item We have a preliminary dyadic file for all similar bill pairs and their alignment scores (this is from the LID approach: each bill is only compared to the 100 most similar ones)
        \item Matt transfering the database to a new server at the moment, it is therefore unavailable. Should be online again sometime today.
    \end{enumerate}
\item Store MALP data on ACI and make sure the identifiers match those in the bill data (FL). 
    \begin{enumerate}
        \item data is on aci
        \item Legislators can be matched by Name, State, Pary and Term. This information should be contained in the database. If not, the open state api has a legislator search method, that returns all necessary information.
    \end{enumerate}
\item Put policy diffusion data in project folder on ACI (BD).
\end{itemize}
